Adaptive group-regularized logistic elastic net regression

### 2019-02-19 docs/manuscript.Rnw
exchanged cross-validation from metabolomics_alzheimer.R example with train/test data setup

@@

	\section{Application}\label{sec:app}

>>>>

% load packages and set options
<<settings, include=FALSE, echo=FALSE>>=
library(cambridge)
opts_knit$set(base.dir="../figs")
opts_chunk$set(fig.align='center', echo=FALSE, fig.path="../figs/", cache=FALSE,
               message=FALSE)
@

% read figure code
<<figures, include=FALSE>>=
read_chunk("../code/figures.R")
@

@@

	\section{Application to metabolomics in alzheimer}\label{sec:app}

<<lines_metabolomics_alzheimer_res1_auc, fig.cap="Cross-validated AUC in alzheimer example using metabolomics class co-data, with a) the full range and b) cut-out", out.width="100%", fig.asp=2/3>>=
@

<<lines_metabolomics_alzheimer_res2_auc, fig.cap="Cross-validated AUC in alzheimer example using quality score co-data, with a) the full range and b) cut-out", out.width="100%", fig.asp=2/3>>=
@

<<lines_metabolomics_alzheimer_res3_auc, fig.cap="Cross-validated AUC in alzheimer example using node degree co-data, with a) the full range and b) cut-out", out.width="100%", fig.asp=2/3>>=
@

<<lines_metabolomics_alzheimer_res4_auc, fig.cap="Cross-validated AUC in alzheimer example using all co-data, with a) the full range and b) cut-out", out.width="100%", fig.asp=2/3>>=
@

<<barplots_metabolomics_alzheimer_res4_auc, fig.cap="Estimated penalty multipliers in alzheimer example using all co-data for a) metabolomics class, b) quality score, and c) node degree", out.width="100%", fig.asp=1>>=
@
